$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-05 paper/paper.tex
Shorten autoref names

\usepackage{hyperref}
%%
%% For section renaming in autoref
\addto\extrasUKenglish{%
\renewcommand{\sectionautorefname}{\S}%
\renewcommand{\subsectionautorefname}{\S}%
\def\exampleautorefname{Ex.}% 
\renewcommand{\figureautorefname}{Fig.}%
}

@@

% Do not use italics in definitions and theorems
\theoremstyle{definition}
\newtheorem{nidefinition}{Definition}
\newtheorem{nitheorem}{Theorem}
\newtheorem{nilemma}{Lemma}

@@

\todo{spellcheck}
\todo{make sure all citations are there}
\todo{rename gradual to something else...}
\todo{Theorem to Thm. Definiton to Def. when referencing. UMA: it's currently set by the lipics class, should we change it?}

@@

\begin{nidefinition}[Types and length-indexed typing contexts]
  A \emph{Type} is either a unit type ($\unit$), a base type ($\base{n}$) or a channel type ($\channel{t}{x}$) defined in \autoref{fig:prectx}.

>>>>

\usepackage{hyperref}

@@

% Do not use italics in definitions and theorems
\theoremstyle{definition}
\newtheorem{nidefinition}{Definition}
\newtheorem{nitheorem}{Theorem}
\newtheorem{nilemma}{Lemma}
\renewcommand{\nitheoremautorefname}{Thm.}%
\renewcommand{\nidefinitionautorefname}{Def.}%
\renewcommand{\nilemmaautorefname}{Lem.}%
\renewcommand{\exampleautorefname}{Ex.}%
\addto\extrasUKenglish{%
  \renewcommand{\sectionautorefname}{\S}%
  \renewcommand{\subsectionautorefname}{\S}%
  \renewcommand{\figureautorefname}{Fig.}%
}

@@

\todo{spellcheck}
\todo{make sure all citations are there}
\todo{rename gradual to something else...}

@@

\begin{nidefinition}[Types and length-indexed typing contexts]
  A \emph{type} is either a unit type ($\unit$), a base type ($\base{n}$) or a channel type ($\channel{t}{x}$) defined in \autoref{fig:prectx}.
